A Fundamental Measure Theory Functional for Hard-Sphere Contact Densities

### 2012-02-21 papers/contact/mod-paper.tex
modified paper changed white bear deriv a bit and added work in progress paper.tex Tested everything on crystal.

\documentclass[letterpaper,twocolumn,amsmath,amssymb,prb]{revtex4-1}
\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage{color}

@@

\affiliation{Department of Physics, Oregon State University, Corvallis, OR 97331}
\author{Jeff Schulte}
\author{Chris Haglund}
\author{Patrick Kreitzburg}
\author{David Roundy}

@@

  \begin{align}
    \frac{\delta A_{HS}}{\delta n_3(\mathbf{r}')} &=
    -\frac{n_0(\mathbf{r}')}{1 - n_3(\mathbf{r}')}
    + \frac{n_1n_2 - \mathbf{n}_{V1}\cdot\mathbf{n}_{V2}}{(1 -
      n_3(\mathbf{r}'))^2}
    + \frac{n_2^3 -
      3n_2\mathbf{n}_{V2}\cdot\mathbf{n}_{V2}}{36\pi}\left(
    \frac{1}{(1-n_3)^2} + 2\frac{\ln(1-n_3)}{n_2^2(1-n_3)}
    \right)
    \\
    \frac{\delta A_{HS}}{\delta n_2(\mathbf{r}')} &=
    \frac{n_1}{1-n_3}
    + 3(n_2^2 - \mathbf{n}_{V2}\cdot\mathbf{n}_{V2})\frac{n_3 +
      (1-n_3)^2\ln(1-n_3)}{
      36\pi n_3^2(1-n_3)^2
    }
    \\
    \frac{\delta A_{HS}}{\delta n_1(\mathbf{r}')} &= \frac{n_2}{1-n_3}
    \\
    \frac{\delta A_{HS}}{\delta n_0(\mathbf{r}')} &=
    -\frac{1}{4\pi R^2} \ln\left( 1 - n_3\right) \\
    \frac{\delta A_{HS}}{\delta \mathbf{n}_{V2}(\mathbf{r}')} &=
    \frac{\mathbf{n}_{V1}}{1-n_3}
    - 6 n_2 \mathbf{n}_{V2} \frac{n_3 +
      (1-n_3)^2\ln(1-n_3)}{
      36\pi n_3^2(1-n_3)^2
    }    \\
    \frac{\delta A_{HS}}{\delta \mathbf{n}_{V1}(\mathbf{r}')} &=
    \frac{\mathbf{n}_{V2}}{1-n_3} \\
    \frac{\delta A_{HS}}{\delta R(\mathbf{r}')} &=
    \frac{n_2}{2\pi R^3} \ln\left( 1 - n_3\right)
    - \frac1{R} \frac{n_1n_2 - \mathbf{n}_{V1} \cdot\mathbf{n}_{V2}}{1-n_3}
  \end{align}

  \begin{align}
    \frac{\delta n_3(\mathbf{r}')}{\delta R(\mathbf{r})} &=
    n(\mathbf{r})\delta(|\mathbf{r}-\mathbf{r}'| - R) \\
    \frac{\delta n_2(\mathbf{r}')}{\delta R(\mathbf{r})} &=
    n(\mathbf{r}) \delta'(|\mathbf{r}-\mathbf{r}'| - R) \\
    \frac{\delta \mathbf{n}_{V2}(\mathbf{r}')}{\delta R(\mathbf{r})} &=
    -\frac{\delta}{\delta R(\mathbf{r})} \mathbf{\nabla}' n_3(\mathbf{r}')
    \\
    &= -\mathbf{\nabla}'
    \left(n(\mathbf{r})\delta(|\mathbf{r}-\mathbf{r}'| - R) \right)
  \end{align}
  These give us some basic tools with which to perform derivatives.

@@

We performed a Monte-Carlo simulation of the hard sphere fluid to
measure the contact density as a function of position for a few simple
geometries.  For each scenario, we compute and compare several
quantities.  We compare the Monte Carlo density with the DFT
prediction.  We also plot Monte Carlo results for the two contact
densities: the contact density evaluated at contact, and the contact
density evaluated at the sphere location.  Alongside these, we plot
the contact density of Fu and Wu~\cite{fu2005vapor-liquid-dft} (or
should it be Yu and Wu\cite{yu2002structures,
  yu2002fmt-dft-inhomogeneous-associating}?), the ``simple contact
density'' from Section~\ref{simple-contact}, and the ``contact density
at sphere'' from Section~\ref{contact-at-sphere}.  In principle, the
functional of Wu (FIXME) should match the CenConDensity, while the DFT
at sphere should match the ConDensity...

>>>>

\documentclass[letterpaper,twocolumn,amsmath,amssymb,jcp,10pt,aip]{revtex4-1}
\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage{color}

@@

\author{Jeff Schulte}
\author{Chris Haglund}
\author{Patrick Kreitzburg}
\author{David Roundy}
\affiliation{Department of Physics, Oregon State University, Corvallis, OR 97331}

@@

  \begin{align}
    \frac{\delta A_{HS}}{\delta n_3(\mathbf{r}')} &=
    \frac{n_0(\mathbf{r}')}{1 - n_3(\mathbf{r}')}
    + \frac{n_1n_2 - \mathbf{n}_{V1}\cdot\mathbf{n}_{V2}}{(1 -
      n_3(\mathbf{r}'))^2}
    - \frac{n_2^3 -
      3n_2\mathbf{n}_{V2}\cdot\mathbf{n}_{V2}}{36\pi}\left(
    \frac{n_3^2-5n_3+2}{n_3^3(1-n_3)^3} + 2\frac{\ln(1-n_3)}{n_3^3}
    \right)
    \\
    \frac{\delta A_{HS}}{\delta n_2(\mathbf{r}')} &=
    \frac{n_1}{1-n_3}
    + 3(n_2^2 - \mathbf{n}_{V2}\cdot\mathbf{n}_{V2})\frac{n_3 +
      (1-n_3)^2\ln(1-n_3)}{
      36\pi n_3^2(1-n_3)^2
    }
    \\
    \frac{\delta A_{HS}}{\delta n_1(\mathbf{r}')} &= \frac{n_2}{1-n_3}
    \\
    \frac{\delta A_{HS}}{\delta n_0(\mathbf{r}')} &=
    -\ln\left( 1 - n_3\right) \\
    \frac{\delta A_{HS}}{\delta \mathbf{n}_{V2}(\mathbf{r}')} &=
    \frac{\mathbf{n}_{V1}}{1-n_3}
    - 6 n_2 \mathbf{n}_{V2} \frac{n_3 +
      (1-n_3)^2\ln(1-n_3)}{
      36\pi n_3^2(1-n_3)^2
    }    \\
    \frac{\delta A_{HS}}{\delta \mathbf{n}_{V1}(\mathbf{r}')} &=
    \frac{\mathbf{n}_{V2}}{1-n_3} \\
    \frac{\delta A_{HS}}{\delta R(\mathbf{r}')} &=
    \frac{n_2}{2\pi R^3} \ln\left( 1 - n_3\right)
    - \frac1{R} \frac{n_1n_2 - \mathbf{n}_{V1} \cdot\mathbf{n}_{V2}}{1-n_3}
  \end{align}

  \begin{align}
    \frac{\delta n_3(\mathbf{r}')}{\delta R(\mathbf{r})} &=
    n(\mathbf{r})\delta(|\mathbf{r}-\mathbf{r}'| - R) \\
    \frac{\delta n_2(\mathbf{r}')}{\delta R(\mathbf{r})} &=
    n(\mathbf{r}) \delta'(|\mathbf{r}-\mathbf{r}'| - R) \\
    \frac{\delta \mathbf{n}_{V2}(\mathbf{r}')}{\delta R(\mathbf{r})} &=
    -\frac{\delta}{\delta R(\mathbf{r})} \mathbf{\nabla}' n_3(\mathbf{r}')
    \\
    &= -\mathbf{\nabla}'
    \left(n(\mathbf{r})\delta(|\mathbf{r}-\mathbf{r}'| - R) \right)
  \end{align}

  ??? Derivatives of the density functions with respect to R.
  n_3(\mathbf{r}') &= \int n(\mathbf{r}'') \Theta(\left|\mathbf{r}' - \mathbf{r}''\right| -R(?)) d\mathbf{r}''

  For the derivation of n_3 in the symmetric case:
  \frac{\delta n_3 (\mathbf{r}')}{\delta R(\mathbf{r})} &=
  \int n (\mthbf{r}'') \delta(|\mathbf{r}' - \mathbf{r}''| - R(\mathbf{r}')) \delta(\mathbf{r}'-\mathbf{r}) d\mathbf{r}''

  R(\mathbf{r}) refers to all the spheres that just touch the point \mathbf{r}

  some stuff times p(\mathbf{r}) &= \int \frac{\deltaA_{HS}}{\delta n_3(\methbf{r}')} 
  \frac{\delta n_3(\mathbf{r}'}{\deltaR(\mthbf{r})} d\mathbf{r}'

  &= \int \frac{\delta A_{HS}}{\delta n_3(\mathbf{r}'} \int n (\mthbf{r}'') \delta(|\mathbf{r}' - \mathbf{r}''| - R(\mathbf{r}')) \delta(\mathbf{r}'-\mathbf{r}) d\mathbf{r}'' d\mathbf{r}'

  &= \frac{\delta A_{HS}}{\delta n_3(\mathbf{r}'} \int n (\mthbf{r}'') \delta(|\mathbf{r} - \mathbf{r}''| - R(\mathbf{r})) d\mathbf{r}''

  &= \frac{\delta A_{HS}}{\deltan_3(\mathbf{r}''} n_2(\mathbf{r})

  So only one n_3(\methbf{r}' is affected, and that's when \mathbf{r}' = \mathbf{r}
  It's affected by all the spheres that \emph{touch} \mathbf{r}'.  To say that R(\mathbf{r})
  changes means that all the spheres touching \methbf{r}'.  And keep in mind these are possible spheres,
  given by densities, not real spheres.  (Write this more good like grammar and stuff.  Look at how to do superscripts)

  And for Assymmetric case:

  \frac{\delta n_3 (\mathbf{r}')}{\delta R(\mathbf{r})} &=
  \int n (\mthbf{r}'') \delta(|\mathbf{r}' - \mathbf{r}''| - R(\mathbf{r}'')) \delta(\mathbf{r}-\mathbf{r}'') d\mathbf{r}''

  &= n (\mthbf{r}) \delta(|\mathbf{r} - \mathbf{r}'| - R(\mathbf{r}))

  here it's a lot of n_3(\mathbf{r}') points that are affected by the sphere changing at R(\mathbf{r}) 
  so sphere is centered at \mathbf{r} here

  Also, here's n_2(\mathbf{r}') for Symmetric case:

  n_2(\mathbf{r}')

  eh.  I'm done for tonight.  Keep going with this.

  \frac{\delta n_3(\mathbf{r}')}{\delta R(\mathbf{r})} &=
    n(\mathbf{r})\delta(|\mathbf{r}-\mathbf{r}'| - R) \\

n_3(\xx) &= \int n(\xx') \Theta(\left|\xx - \xx'\right| - R) d\xx' \\
  n_2(\xx) &= \int n(\xx') \delta(\left|\xx - \xx'\right| - R) d\xx'

  These give us some basic tools with which to perform derivatives.

@@

We performed a Monte-Carlo simulation of the hard sphere fluid to
measure the contact density as a function of position for a few simple
geometries.  For each scenario, we compute and compare several
quantities.  We compare the Monte Carlo density with the DFT
prediction.  We also plot Monte Carlo results for the two contact
densities: the contact density evaluated at contact, and the contact
density evaluated at the sphere location.  Alongside these, we plot
the contact density of Yu and
Wu~\cite{yu2002fmt-dft-inhomogeneous-associating}, the contact density
of Gross~\cite{gross2009density}, and the ``contact density at
sphere'' from Section~\ref{contact-at-sphere}.  In principle, the
functional of Yu (FIXME) should match the CenConDensity, while the DFT
at sphere should match the ConDensity...
